---
title: "Classify with a fast.ai model from R level"
output: html_notebook
---

In this notebook we use a model trained in fast.ai (a wrapper on PyTorch, a Machine Learning library  in Python).

# Imports and setup

```{r echo=T, results='hide'}
# import R libraries
library(reticulate)

library(tibble)
library(tidyr)
library(stringr)
library(jpeg)
library(knitr)
library(dplyr)
```

Load the Python environment in which we can execute the model
```{r}
use_python('/anaconda3/envs/fastai_in_R/bin/python', required=TRUE)
use_condaenv('fastai_in_R')
```

I am using a Conda environment setup (on a Mac) with the following lines
```
conda create fastai_in_R python=3.7
conda activate fastai_in_R

conda install pytorch torchvision -c pytorch
pip install fastai
pip install opencv-python
```

Import Python libraries
```{r}
fastai <- import('fastai.vision')
```

# Constants

```{r}
ModelPath <- file.path(getwd(), 'fire_model_script', 'model')
ModelFilename <- 'trained_model.pkl'
DataFunExamples <- file.path(getwd(), 'fire_model_script', 'images_fun_examples')
```

# Get images list
```{r}
TestImgList <- list.files(DataFunExamples, full.names=TRUE)
print(str_glue('Found {length(TestImgList)} images in folder: {DataFunExamples}.\nOne of them is {TestImgList[[5]]}:'))
include_graphics(TestImgList[[5]])
```
# Load model
```{r}
print(str_glue('Loading model: {ModelPath}/{ModelFilename}.\nRunning inference on {length(TestImgList)} images.'))
learn <- fastai$load_learner(ModelPath, ModelFilename, test=TestImgList)
print(str_glue('Model loaded.\nModel uses {length(learn$data$classes)} classes: {toString(learn$data$classes)}'))
```
# Run inference
```{r}
InferenceStart <- Sys.time()
print(str_glue('Starting inference. time={InferenceStart}'))
Preds <- learn$get_preds(ds_type=fastai$DatasetType$Test)[[1]]
InferenceStop <- Sys.time()
print(str_glue('Inference complete. It took {InferenceStop - InferenceStart}.'))
```

# Prepare predictions
```{r}
Classes <- learn$data$classes
PredsDataFrame <- data.frame(Preds$numpy(), row.names=TestImgList)
colnames(PredsDataFrame) <- Classes
PredsDataFrame
```

```{r}
PredsTop <- PredsDataFrame %>% 
  rownames_to_column() %>%
  gather(top_prediction, score, -rowname) %>%
  group_by(rowname) %>% 
  filter(rank(-score) == 1) 
PredsTop
```

# Plot predictions
```{r}
par(mfrow = c(2, 3), mar = c(0, 0, 3, 0));
invisible(sapply(seq_along(PredsTop$rowname), function(i) {
  plot.new()
  img <- readJPEG(PredsTop$rowname[i])
  dims <- dim(img)
  aspect <- dims[1] / dims[2]
  plot.window(xlim=c(0, 1), ylim=c(0, 1), asp=aspect)
  rasterImage(img, 0, 0, 1, 1)
  title(paste0('prediction: ', PredsTop$top_prediction[i], ', score: ', round(PredsTop$score[i], 2)))
}))
```
